Three Algorithms for Merging Navigable Graphs

### 2024-10-09 paper/main.tex
Rewrite introdution section

>>>>

\section{Introduction}
In recent years, navigable small-world graphs have become a cornerstone of efficient approximate nearest neighbor (ANN) search in high-dimensional spaces, a problem prevalent in fields such as recommendation systems, image retrieval, and natural language processing. Algorithms like Hierarchical Navigable Small World (HNSW) and its predecessor Navigable Small World (NSW) provide a robust and scalable framework for organizing data into graph structures that support fast similarity searches. However, one limitation inherent to these methods is the lack of a natural mechanism for node deletion, making the need for merging and compacting graphs crucial for maintaining the efficiency and accuracy of the search index over time.

The HNSW algorithm, widely adopted for its performance and scalability, supports dynamic insertions but lacks native support for node deletion. As databases grow and evolve, some nodes become outdated or irrelevant, requiring a process to filter out these deleted vertices. Merging operations allow for a form of "data compaction," where the graphs from two or more databases are merged, and nodes marked for deletion are omitted from the final structure. This process not only improves space efficiency but also enhances the accuracy of future searches by eliminating superfluous data points.

In this work, we propose three novel algorithms designed to efficiently merge navigable graphs, focusing on HNSW but extending applicability to other graph-based data structures like NSW, NSG. The merging algorithms—"Naive Merge," "Merge1," and "Merge2"—offer progressively advanced methods to combine graphs while preserving the properties that make navigable graphs effective for nearest neighbor search. These methods ensure that the resulting merged index excludes deleted nodes and maintains the structural integrity needed for fast search operations.
